\section{Introduction}

\subsection{Problem Statement}

\subsubsection{Software Testing Perspective}

When testing code consuming numerical data, it is common to use random transforms to produce synthetic data sets for testing.

However, this introduces the probability that any given run of the test will fail to catch edge cases, or fail due to a specific random seed.

The problem we address in this paper is: \textit{How can we efficiently and reliably estimate the required number of test runs needed to establish the absence of failures with a certain confidence level, given an unknown relationship between the input data and test failure, and knowledge of the distribution of the input data?}

\subsubsection{Mathematical Setup}

    \subsubsubsection{Population and Sets}

    Each input to the function under test consists of a fixed-size set of elements $X^{(j)}$.

    Let $P = \{ X^{(1)}, X^{(2)}, \dots \}$ be a countably infinite population of sets, representing all possible inputs for the function under test $F$. 
    
    \[
        X^{(j)} = \{ X_0^{(j)}, X_1^{(j)}, \dots, X_{n-1}^{(j)} \}, \quad j \in \mathbb{N}.
    \]

    Each element $X_i^{(j)}$ is drawn i.i.d. and has probability $p$ of being an \textbf{outlier} (an event we denote $O_i^{(j)} = 1$ if $X_i^{(j)}$ is an outlier, $0$ otherwise):
    \[
        \Pr[ O_i^{(j)} = 1 ] = p
    \]

    Where an \textbf{outlier} is defined as an element exhibiting characteristics associated with an increased likelihood of test failure.

    \subsubsubsection{Blackbox Function}

    There is a function under test, which we treat as a blackbox function
    \[
        F : \mathcal{X} \to \{0,1\}, \quad F(X^{(j)}) =
        \begin{cases}
        1 & \text{if set passes} \\
        0 & \text{if set fails}
        \end{cases}
    \]

    We assume there exists a relationship between the presence of outliers in ( $X^{(j)}$ ) and failure, but the exact nature of this relationship is unknown:
    \[
        \text{unknown mapping } F(X^{(j)}) \sim f(O_0^{(j)}, \dots, O_{n-1}^{(j)})
    \]

    \subsubsubsection{Sampling Problem}

    Let ( S \subseteq P ) be the subset of sets actually observed/tested.

    Define the event
    \[
        E = \exists X^{(j)} \in S : F(X^{(j)}) = 0
    \]

    i.e., "we observe at least one failing set."

    The goal is:

    \[
        \text{ Find the minimal } |S| \text{ such that } \Pr[E] \ge \gamma
    \]

    where ( \gamma \in (0,1) ) is a target confidence (e.g., 0.95).

    Corresponding to the problem of finding the minimum number of samples needed to have a confidence of at least ( \gamma ) that we have observed at least one failing set, given the unknown relationship between outliers and failure, and the probability of outliers in the population.


\subsection{Comparison to Other Methods}

Below we outline existing approaches to the problem, and their limitations compared to the proposed BOAST method.

\subsubsection{Common Approaches in Industry}

    This problem is commonly addressed in industry using heuristics such as fixed-budget testing, adversarial thinking, or fuzzing, depending on the specific context of the test and the resources available.

    \subsubsubsection{Fixed-budget testing}

        \paragraph{Approach} Select a large fixed number of iterations $k$ based on heuristics, and run the test for that many iterations \cite{myers2011art}.

        \paragraph{Advantages} This method is simple and easy to implement.

        \paragraph{Limitations} It does not provide any guarantees about the confidence level of detecting failure and as such can result in a number of iterations that is either too low (leading to false confidence in the reliability of the code), or too high (leading to wasted computational resources). Additionally, in the case of the absence of failure, this method provides no ability to stop early, and thus can waste resources.

    \subsubsubsection{Worst-case / adversarial thinking}

        \paragraph{Approach} Design tests to specifically target edge cases and potential failure modes, rather than relying on random sampling.

        \paragraph{Advantages} Very effective for regression testing (i.e., testing for specific known issues) and can be more efficient than random sampling if the failure modes are well understood.

        \paragraph{Limitations} Cannot provide a comprehensive assessment of the code's reliability, and can be time-consuming to design and implement. Additionally, is not effective in catching unknown failure modes or edge cases that were not anticipated during test design.

    \subsubsubsection{Fuzzing}

        \paragraph{Approach} Generate random or semi-random inputs to test the code, with the goal of uncovering edge cases and potential failure modes.

        \paragraph{Advantages} Very comprehensive; can be effective in catching a wide range of issues, including those that were not anticipated during test design. Can also be designed with stopping criteria based on observed pass/fail ratios, which can provide some efficiency benefits compared to fixed-budget testing.

        \paragraph{Limitations} Computationally expensive, as it requires a large number of test iterations to achieve a high confidence level of detecting failure. Fuzzing is also not normally suitable for use in CI pipelines or other time-sensitive contexts, as it requires a large number of iterations. Additionally, it does not take into account domain-specific knowledge about the data or the code under test, which can lead to inefficient testing and missed failure modes.

    \subsubsection{SPRT (Sequential Probability Ratio Test)}

        \paragraph{Approach} A statistical method for testing a hypothesis by evaluating the likelihood ratio of observed data under two competing hypotheses, and stopping when the ratio exceeds a certain threshold \cite{wald1945sequential}.

        \paragraph{Advantages} Provides a rigorous statistical framework for testing hypotheses and can be more efficient than fixed-budget testing. It also attempts to minimize the expected number of samples needed to reach a conclusion.

        \paragraph{Limitations} For noisy data, SPRT can theoretically require an infinite number of samples to reach a conclusion, as the likelihood ratio may never exceed the threshold. Additionally, SPRT does not take into account domain-specific knowledge about the data or the code under test, which can lead to inefficient testing and missed failure modes.

\subsubsection{Recent Literature}

    \subsubsubsection{An Efficient Adaptive Sequential Procedure for Simple Hypotheses with Expression for Finite Number of Applications of Less Effective Treatment}

        \paragraph{Approach} Unlike SPRT, this method addresses the problem of drift in case of noisy data, reducing the probability of infinite sampling. It does so by introducing an adaptive procedure that adjusts the testing strategy based on observed data \cite{kundu2025efficientadaptivesequentialprocedure}.

        \paragraph{Advantages} Just as rigorous as SPRT, while addressing the excessive sampling problem in the case of noisy data. Additionally it introduces a closed-form expression for the expected number of inferior allocations, allowing for precise estimation of the "cost of testing" in live environments.

        \paragraph{Limitations} Like SPRT, this method does not take into account domain-specific knowledge about the data or the code under test, which can lead to inefficient testing and missed failure modes. Additionally, while it addresses the issue of infinite sampling in noisy data, it may still require a large number of samples to reach a conclusion in cases where the data is particularly noisy or the difference between hypotheses is small, and as such may not be suitable for use in time-sensitive contexts such as CI pipelines.

    \subsubsubsection{Classifier-Based Nonparametric Sequential Hypothesis Testing}

        \paragraph{Approach} A hypothesis testing method that uses a classifier to distinguish between two distributions, and applies sequential testing to determine which distribution is more likely \cite{hsu2026classifierbasednonparametricsequentialhypothesis}.

        \paragraph{Advantages} Adaptable to complex data distributions, and claims to identify the ground-truth almost surely.

        \paragraph{Limitations} Requires training a classifier, which can be computationally expensive and often domain or application specific. Additionally, the method does not provide guarantees on the number of samples needed to reach a conclusion, and can be inefficient in cases where the distributions are similar. The use of a classifier also introduces computational overhead and potential for overfitting in the training process.

    \subsubsubsection{Conservative Software Reliability Assessments Using Collections of Bayesian Inference Problems}

        Building on the work of Salako and Muhammad \cite{salako2025conservativesoftwarereliabilityassessments}, who demonstrate that conservative software reliability testing requires moving away from singular statistical frameworks in favor of mixed approaches, this paper proposes a hybrid Bayesian-frequentist approach to the problem of conservative software reliability testing. While the work of Salako and Muhammad utilizes a collection of Bayesian methodologies, our method employs an intentionally conservative Bayesian component to inform the stop criterion of a sequential frequentist test, which we demonstrate to be effective in controlling computational cost while maintaining reliable estimates of failure probability.